\begin{resume}


% \section*{发表的学术论文} % 发表的和录用的合在一起

%   \begin{enumerate}[{[}1{]}]
%   \addtolength{\itemsep}{-0.36\baselineskip}
%   \settowidth\labelwidth{1.1cm}
%   \setlength{\labelsep}{0.4em}
%   \setlength{\itemindent}{\labelwidth+\labelsep+0.4em}
%   \setlength{\leftmargin}{0em}
%   \addtolength{\itemsep}{-.36\baselineskip}%缩小条目之间的间距，下面类似
%   \item \textbf{第一作者}. A Framework for Memory Oversubscription Management in Graphics Processing Units.
%         In 24th International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS'19), 2019 （CCF A类会议）
%   \item \textbf{第一作者}. A Dynamic and Proactive GPU Preemption Mechanism using Checkpointing.
%         In IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), 2019 （CCF A类期刊）
%   \item \textbf{第一作者}. PEP: Proactive Checkpointing for Efficient Preemption on GPUs.
%         In 55th Design Automation Conference (DAC), 2018 （CCF A类会议）
%   \item \textbf{第一作者}. DLL: A dynamic latency-aware load-balancing strategy in 2.5D NoC architecture.
%         In 34th IEEE International Conference on Computer Design (ICCD), 2016 （CCF B类会议）
%   \item \textbf{第一作者}. Overcoming and Analyzing the Bottleneck of Interposer Network in 2.5 D NoC Architecture.
%         In Advanced Computer Architecture (ACA), 2016
%   \item \textbf{第一作者}. 三维片上网络体系结构研究综述. 计算机学报. 2016.  
%   \item \textbf{第一作者}. Express Ring: a multi-layer and non-blocking NoC architecture
%         In IEICE Electronics Express, 2015
%   \item \textbf{第三作者}. Fairness-oriented and location-aware NUCA for many-core SoC
%         In 11th IEEE/ACM International Conference on Networks-on-Chip (NOCS), 2017
%   \item \textbf{第三作者}. Fairness-oriented switch allocation for networks-on-chip.
%         In 30th IEEE International System-on-Chip Conference (SOCC), 2017
%   \item \textbf{第三作者}. A high performance reliable NoC router.
%         In Integration, the VLSI Journal, 2017
%   \item \textbf{第三作者}. A Low-Cost and Low-Latency Heterogeneous Ring-Chain Network for GPGPUs.
%         In 34th IEEE International Conference on Computer Design (ICCD), 2016
%   \item \textbf{第五作者}. Adaptive remaining hop count flow control: Consider the interaction between packets.
%         In 20th Asia and South Pacific Design Automation Conference (ASP-DAC), 2015

%   \end{enumerate}

\section*{发表的学术论文} % 发表的和录用的合在一起

  \begin{enumerate}[{[}1{]}]
  \addtolength{\itemsep}{-0.36\baselineskip}
  \settowidth\labelwidth{1.1cm}
  \setlength{\labelsep}{0.4em}
  \setlength{\itemindent}{\labelwidth+\labelsep+0.4em}
  \setlength{\leftmargin}{0em}
  \addtolength{\itemsep}{-.36\baselineskip}%缩小条目之间的间距，下面类似
  \item \textbf{Chen Li}, Rachata Ausavarungnirun, Christopher J. Rossbach, Youtao Zhang, Onur Mutlu, Yang Guo, and Jun Yang. A Framework for Memory Oversubscription Management in Graphics Processing Units.
        In 24th International Conference on Architectural Support for Programming Languages and Operating Systems (ASPLOS'19), 2019 （CCF A类会议）
  \item \textbf{Chen Li}, Andrew Zigerelli, Jun Yang, Youtao Zhang, Sheng Ma, Yang Guo. A Dynamic and Proactive GPU Preemption Mechanism using Checkpointing.
        In IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems (TCAD), 2019 （CCF A类期刊）
  \item \textbf{Chen Li}, Andrew Zigerelli, Jun Yang, Yang Guo. PEP: Proactive Checkpointing for Efficient Preemption on GPUs.
        In 55th Design Automation Conference (DAC), 2018 （CCF A类会议）
  \item \textbf{Chen Li}, Sheng Ma, Lu Wang, Zicong Wang, Xia Zhao, Yang Guo. DLL: A dynamic latency-aware load-balancing strategy in 2.5D NoC architecture.
        In 34th IEEE International Conference on Computer Design (ICCD), 2016 （CCF B类会议）
  \item \textbf{Chen Li}, Zicong Wang, Lu Wang, Sheng Ma, Yang Guo. Overcoming and Analyzing the Bottleneck of Interposer Network in 2.5 D NoC Architecture.
        In Advanced Computer Architecture (ACA), 2016
  \item \textbf{李晨}，马胜，王璐，郭阳. 三维片上网络体系结构研究综述. 计算机学报. 2016.  
  \item \textbf{Chen Li}, Sheng Ma, Shenggang Chen, Yang Guo. Express Ring: a multi-layer and non-blocking NoC architecture
        In IEICE Electronics Express, 2015
  \item Zicong Wang, Xiaowen Chen, \textbf{Chen Li}, Yang Guo. Fairness-oriented and location-aware NUCA for many-core SoC
        In 11th IEEE/ACM International Conference on Networks-on-Chip (NOCS), 2017
  \item Zicong Wang, Xiaowen Chen, \textbf{Chen Li}, Yang Guo. Fairness-oriented switch allocation for networks-on-chip.
        In 30th IEEE International System-on-Chip Conference (SOCC), 2017
  \item Lu Wang, Sheng Ma, \textbf{Chen Li}, Wei Chen, Zhiying Wang. A high performance reliable NoC router.
        In Integration, the VLSI Journal, 2017
  \item Xia Zhao, Sheng Ma, \textbf{Chen Li}, Lu Wang, Zhiying Wang. A Low-Cost and Low-Latency Heterogeneous Ring-Chain Network for GPGPUs.
        In 34th IEEE International Conference on Computer Design (ICCD), 2016
  \item Peng Wang, Sheng Ma, Hongyi Lu, Zhiying Wang, \textbf{Chen Li}. Adaptive remaining hop count flow control: Consider the interaction between packets.
        In 20th Asia and South Pacific Design Automation Conference (ASP-DAC), 2015

  \end{enumerate}

\end{resume}
